\autsection{Budget}{Daniel Santiago}
\label{sec:Budget}

Accurate estimates of cost is was always extremely important for ensuring that the team
did not go over budget. Since this is a software project, the majority of the
cost was attributed to Software Developers and Human Resources. Development costs
remained low since computer workstations and an internet connection was
provided at all times. An Amazon EC2 web services instance was purchased for the development and the final deployment of the product.

\subsection{Project Cost}
The total estimated cost of the project is \$42,791.87 plus recurrent costs
after deployment. The broke down details follow.

\subsubsection{List of Components}
\begin{itemize}
\item 1 Workstation minimum (\$0 - Provided by team). The workstations are
needed for software development.
\end{itemize}

\subsubsection{Recurring Costs after Deployment}
\begin{itemize}
\item Amazon Web Services EC2 (\$528 per year). The service is needed for
deploying the project. The service is the most reasonable for the project, since
it is able to scale automatically and the pricing changes depending on the
amount of server usage.
\begin{itemize}
\item EC2 Instance specs: C1.Medium (Compute-optimized)
\item Intel Xeon - 2 vCPU, 350GB, 4GB RAM, \$0.145 per Hour
\item Auto-Scaling: \$0.025 per Elastic Load Balancer-hour, \$0.008 per GB of data processed by an Elastic Load Balancer
\end{itemize}

%We have to do some math and mention how that math is considering x amount of
% active instances.

\item Symantec Verisign 256 bit SSL certificate (\$400 per year). The
certificate is needed for ensuring secure connections via HTTPS.
\end{itemize}

\subsubsection{Human Resources}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|c|p{3.5cm}|p{1.5cm}|p{1cm}|p{1cm}|p{1.5cm}|p{2cm}|}
 \caption{Human Resources} \\
   \hline
  
  \centering Employee & Position & Annual Salary & Hourly Wage & Hours per Week & Working Weeks & Payment \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Employee & Position & Annual Salary & Hourly Wage & Hours per Week & Working Weeks & Payment \\
	\hline \hline \endhead
  
  \endfoot  
%TODO change to 9 weeks (16/sept - 15/nov)
    Nelián & Project Manager and Software Engineer & \$55,000  & \$26.44  & 20    & 9    & \$4,759.61  \\ \hline
    Samuel & Software Engineer & \$45,000  & \$21.63  & 20    & 9    & \$3,894.23  \\ \hline
    Daniel & Software Engineer & \$45,000  & \$21.63  & 20    & 9    & \$3,894.23  \\ \hline
    \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total}} & \multicolumn{1}{l}{\$12,548.07}            
\end{longtable}

\subsubsection{Employee Fringe Benefits}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \caption{Employee Fringe Benefits} \\
   \hline
  
  \centering Sick Leave (0.5 days per month) & Paid Vacation (5 days) & Employee Health Insurance & Employee Fringe Benefits \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Sick Leave (0.5 days per month) & Paid Vacation (5 days) & Employee Health Insurance & Employee Fringe Benefits \\
	\hline \hline \endhead
  
  \endfoot  

    \$800 & \$2,000 & \$2,000 & \$4,800  \\ \hline
    \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total}} & \multicolumn{1}{l}{\$14,400}
\end{longtable}

\subsubsection{Overhead Hours}

\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|c|c|c|}
 \caption{Overhead Hours\label{overheadHours}} \\
   \hline
  
  \centering Task & Overhead Hours & Total Hours (3 members) \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Task & Overhead Hours & Total Hours (3 members) \\
	\hline \hline \endhead

 \endfoot  

	Team Meetings & 49 & 147 \\ \hline
	Writing Reports & 96 & 288 \\ \hline
	Course Meetings & 65 & 195 \\ \hline	  
	Presentations & 4 & 12 \\ \hline
  \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Non-billable Hours}} & \multicolumn{1}{l}{120}  \\
  \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total Hours}} & \multicolumn{1}{l}{642}  \\
  \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total}} & \multicolumn{1}{l}{\$14,915.80}
    \end{longtable}
    
%% some extra stuff
The project expenditure totaled at \$42,081.23. This total
includes a cost of \$217.36 for the development Amazon EC2 Instances and the 9 billable weeks that have elapsed since the start of the project. What saved money for Team Aguacate was by using a free self signed SSL certificate, and by lowering the Amazon EC2 instance costs. The team managed to save 1.66\% of the initial budget.
