\part*{Executive Summary}

Assignments for Software Engineering classes have particular characteristics
that make them time-consuming to grade by professors and teaching assistants
(TA). In the majority of cases, they are handed in electronically. The grader
then runs the code with some specific input to verify its correctness. Students
might choose to use different programming languages, different IDEs, and
different tests, making grading even more difficult. Additionally, many students
write code in different styles, which may make it harder to read for a person
that has been accustomed to a particular coding style. Furthermore,
communication between the grader and the student may be slow, often relying in
sluggish e-mail exchanges. All of this makes grading software assignments an
enduring and tedious task.

Panda Code Reviews has been modularly designed following industry leading
standards and using the newest technology for web applications development. It
was built to be a fully hosted web application in the cloud that
eliminates many of the difficulties that come with grading software assignments.
The application hosts repositories that contain students' code. When a
student submits code for an assignment, the system notifies the grader and
automatically runs test cases previously specified by the grader.
Finally, the grader will have the option to assign a
grade to the student.

The initially estimated budget was \$42,791.87. An actual budget of \$42,081.23 was spent for the development of the project; a 1.66\% decrease.

%% Presents actual or potential customers/market