\autsection{Introduction}{Samuel Rodríguez}

Most educational institutions manually grade coding assignments completed by
students. Manual evaluation of code takes a great deal of time and is prone to
bad evaluations due to the substantial amount of different ways a program can be
written. Sometimes, this leads the grader to only evaluate the program's output
based on a specific input.

%% la porqueria de hoja de evaluacion dice que hay que poner toda la literatura
%% que tiene que ver con absolutamente todos los aspectos del proyecto en la intro.
%% look for this in proposal.
Panda Code Reviews is a web-based automatic code grader. The main objective of
this product is to eliminate the difficulties that come with grading software assignments.
The application design is shown throughout this report. Implementation
phase has been finished and the production version of the service is already
residing on the cloud. No changes were made to the initially proposed design;
there only were some minor changes in schedule that did no affect the final deadline
of the delivery of the product.

%% chequeate bien este parrafo porque esta medio sketchy.
%% this is the organization of the rest of the report.
The report contains a schedule analysis that explains the changes within the
proposed timeline, followed by a review of the current expenses and budget
analysis. The following section contains the project technical plan, which
includes the software design. An overview of the system is given, followed by a
more detailed breakdown of the software components. The two major components of
the software are the front end and the back end, which are broken down and
explained in detail. Finally, this report indicates proposal deviations and a
collection of appendices in order to provide more detail for the different
design specifications.
