\autsection{Assessment Methods}{Nelián Colón}

Progress on each part will be defined depending on the current phase of design,
implementation, testing of each individual component, and of the integration of
the system as shown in Table~\ref{asses}. Team Aguacate will work in sprints and
each task will have a weight according to their priority, which will be decided
in the sprint planning meeting. Progress within major tasks will be measured by
the weight of the tasks done. To help manage the project and collect information
on each member's individual progress on their tasks, the project manager decided
to use Zoho Projects. This web tool allows to divide tasks, and lets each team
member specify how much they have progressed in a specific task. The team will
also have a Git repository where all the code that has been written will be
stored, so that progress can also be monitored from the amount of code already
written.

\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|c|m{7.5cm}|c|}
 \caption{Progress Assessment Overview \label{asses}} \\
   \hline
  
  \centering Description & Progress Definition & Progress \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Description & Progress Definition & Progress \\
  \hline \hline \endhead
  
  \endfoot  
  
  Web Front-end Design & Design phase is complete. & 15\%\\ \hline   
  Back-end Server Design & Design phase is complete. & 25\%\\ \hline   
  Accounts \& Repositories Design & Design phase is complete. & 5\%\\ \hline 
  Implementation & Individual modules are complete & 30\%\\ \hline 
  Testing & Unit testing is complete. Implementation phase is complete. & 15\%\\ \hline
  Integration & System integration and testing is complete. & 15\%\\ \hline
  \textbf{Total} & Project is complete & 100\% \\ \hline   
  \end{longtable}