\autsection{Budget}{Samuel Rodríguez}
\label{sec:Budget}

Accurate estimates of cost is extremely important for ensuring that the team
does not go over budget. Since this is a software project, the majority of the
cost is attributed to Software Developers and Human Resources. Development costs
remain low as long as computer workstations and an internet connection is
provided. At the last step of the development of the project, an Amazon Web
Services EC2 account needs to be purchased in order to deploy the system.

\subsection{List of Components}

\begin{itemize}
\item 2 Workstations minimum (\$0 - Provided by team). The workstations are
needed for software development.
\item Amazon Web Services EC2 (\$44 monthly after deployment). The service is
needed for deploying the project. The service is the most reasonable for the
project, since it is able to scale automatically and the pricing changes
depending on the amount of server usage.

\end{itemize}

\subsection{Project Cost}
\subsubsection{Human Resources}
\begin{center}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|c|p{3.5cm}|p{1.5cm}|p{1cm}|p{1cm}|p{1.5cm}|p{2cm}|}
 \caption{Human Resources} \\
   \hline
  
  \centering Employee & Position & Annual Salary & Hourly Wage & Hours per Week & Working Weeks & Payment \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Employee & Position & Annual Salary & Hourly Wage & Hours per Week & Working Weeks & Payment \\
	\hline \hline \endhead
  
  \endfoot  

    Nelián & Project Manager and Software Engineer & \$55,000  & \$26.44  & 20    & 15    & \$7,932.69  \\ \hline
    Samuel & Software Engineer & \$45,000  & \$21.63  & 20    & 15    & \$6,490.38  \\ \hline
    Daniel & Software Engineer & \$45,000  & \$21.63  & 20    & 15    & \$6,490.38  \\ \hline
    \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total}} & \multicolumn{1}{l}{\$20,913.46}  \\
          
           \end{longtable}
\end{center}

\subsubsection{Employee Fringe Benefits}
\begin{center}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \caption{Employee Fringe Benefits} \\
   \hline
  
  \centering Sick Leave (0.5 days per month) & Paid Vacation (5 days) & Employee Health Insurance & Employee Fringe Benefits \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Sick Leave (0.5 days per month) & Paid Vacation (5 days) & Employee Health Insurance & Employee Fringe Benefits \\
	\hline \hline \endhead
  
  \endfoot  

    \$800 & \$2,000 & \$2,000 & \$4,800  \\ \hline
    \multicolumn{1}{l}{}      & \multicolumn{1}{l}{}      & \multicolumn{1}{l}{\textbf{Total}} & \multicolumn{1}{l}{\$14,400}  \\
          
           \end{longtable}
\end{center}

\subsubsection{Overhead Hours}

\begin{center}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|c|c|c|}
 \caption{Overhead Hours\label{overheadHours}} \\
   \hline
  
  \centering Task & Overhead Hours & Total Hours (3 members) \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Task & Overhead Hours & Total Hours (3 members) \\
	\hline \hline \endhead

 \endfoot  

	Team Meetings & 49 & 147 \\ \hline
	Writing Reports & 96 & 288 \\ \hline
	Course Meetings & 65 & 195 \\ \hline	  
	Presentations & 4 & 12 \\ \hline
    \end{longtable}
\end{center}
