\autsection{Objectives}{Samuel Rodríguez}
% SMART objectives:
% Specific, Measurable, Agreed-upon, realistic, time-bound

\subsection{Objectives Outcomes and Metrics}
To build the complete code review system, the team will accomplish the following
objectives by November 15, 2013:

\begin{itemize}
\item Create a visually modern front end interface that includes an account
manager, repository manager, test manager, source code viewer with syntax
highlighter, source code annotator and source code quality analyzer.

\item Build a testing framework that will run tests for programs written in C++,
Java and Javascript.

\item Create a test coverage analyzer and integrate it with the testing
framework.

\item Construct a code quality framework that will include linters for Java
and Javascript.

\item Create an accounts and Git repository back end module.

\item Create a cloud based back end REST API for communications between the
front end interface and both the testing and code quality frameworks.

\item Deploy the system in Amazon Elastic Compute Cloud systems (Amazon Web
Services EC2).

\end{itemize}
\subsection{Deliverables}

The deliverables for this project will be a cloud based web application with the
featured Code Review tool by November 15, 2013. The Code Review tool will be
able to highlight syntax, run test cases, and analyze code quality for C++, Java
and Javascript source files. It will also be able to run programs with an input
specified by the grader, and will be able to compare the program's output with
an output specified by the grader. The web application will be fully hosted in a
provided cloud infrastructure without additional installation or configuration.
Grader and student accounts will be able to be created by the client, and it
will be able to be used immediately after launch.

