\autsection{Personnel}{Nelián Colón}

This section discusses the skills required and how  the team will be meeting
those necessities. To see the team composition and a biography of each of
the members, look at Appendix~\ref{sec:bios}.

\subsection{Skills Required}

Table~\ref{skills} shows a list of skills required for each of the tasks mentioned before, the task lead and the relevant experience he/she has.

\begin{center}
\setlength{\extrarowheight}{1.5pt}
  \begin{longtable}{|m{3cm}|m{5cm}|c|m{5cm}|}
 \caption{Tasks and Skills Matching \label{skills}} \\
   \hline
  
  \centering Task Title & Skills Required & Lead & Experience \\
  \hline \hline \endfirsthead
  
     \hline

	\centering Task Title & Skills Required & Lead & Experience \\  
	\hline \hline \endhead
  
  \endfoot  
  
  Project Management and Team Organization & People skills and leadership & Nelián & Leadership positions in student organizations, leader in previous class projects\\ \hline
  Web Front-end & Knowledge of HTML, JavaScript, graphics and web standards & Samuel & Google internship experience in front-end web development\\ \hline
  Back-end Server & Knowledge of HTTP and Restful API, MongoDB and Node.js & Daniel & Freelance projects, hackathons and past internship experiences exposure to emerging web technologies \\ \hline
  Test Framework & Knowledge of test driven development with code standardization and Coverage, compilers, processes and threads & Daniel & Past internship experience exposure to code quality and performance analysis\\ \hline
  Accounts \& Repositories & Knowledge of repositories and Data Bases & Nelián & Database Systems course, and version control and source code management
technologies exposure\\ \hline
   \end{longtable}
\end{center}

\subsection{Training Needs}
For the development of this project, the members of the team have enough experience to work with their respective tasks. Should they find something they do not know how to do, they are responsible of
learning about the new technologies they have to work on, self train themselves through courses or readings, and ask for help when needed. 

The intent of this product is to make it easy to use. The end users of this product will not need any special training to be able to use it.

\subsection{Consultancy Resources}
For this project, the team has identified some key consultants to help with its progress. These include Teaching assistants to get feedback about our product (their needs and their opinion about our solution), a Database management and Web Development expert, and a Front-End Web development expert.

\begin{itemize}
\item Front-End Web Development
\begin{itemize}
\item Consultant Expert: César Andreu
\end{itemize}
\item Teaching Assistant feedback
\begin{itemize}
\item Consultant Expert: Jesús E. Luzón
\item Consultant Expert: José Santuche
\item Consultant Expert: Zach Cross
\item Consultant Expert: Divit Singh
\end{itemize}
\item Database Management and Web Development
\begin{itemize}
\item Consultant Expert: Dr. Manuel Rodríguez
\end{itemize}
\end{itemize}

\subsection{Legal Requirements and Conditions}

For this project, there are no legal requirements or conditions related to
personnel needed for the project.