\autsection{Risk Management}{Daniel Santiago}
\begin{center}
\setlength{\extrarowheight}{1.5pt}
    \begin{longtable}{|m{5cm}|c|c|m{7cm}|}
 \caption{Work Distribution Table} \\
     \hline
    
    \centering  Risk & Probability & Impact & Actions \\
    \hline \hline \endfirsthead
    
         \hline

	\centering  Risk & Probability & Impact & Actions \\    
	\hline \hline \endhead
    
    \endfoot  
Loss of Data    & Low           & Low      & Backup repository will be used to store code and data. Images of VMs will be on the cloud.       \\ \hline
Developer's Workstation Breaks  & Medium           & Medium      & University's computers will be used instead. If necessary and budget allows it, developer buys new workstation.       \\  \hline
    Hosting Infrastructures Goes Down    & Low           & High      & Work will still be performed on local workstations and as soon as infrastructure is back online, deployment is done with never version.       \\  \hline
    Natural Disaster    & Medium           & Low      & Using revisioned repository each developer can safely work remotely. Moreover, if possible online meetings will be held.       \\  \hline
    Team Member Gets Sick    & Medium           & Medium      & If team member is unable to work, task distribution will be delegated considering tasks priorities and their ability to block other tasks.       \\  \hline
    Team Member Withdraws From Class   & Low           & High      & Agreement has been reach that if team member withdraws from class they must still collaborate on the their respective project part. If unwilling to cooperate, task delegation will have to be performed. Higher working hours will be needed.       \\  \hline
    Out of Budget    & Low           & Medium      & Funding will be needed from different source. Team's personal money will be used as last resort.       \\  \hline
\end{longtable}
\end{center}
