\autsection{Introduction}{Samuel Rodríguez}

%reexamines problem description and project objectives considering current status

%presents and analyzes any new literature or aspects of the project that have arisen after the proposal

%presents the organization of the report

%TODO add objetives?
Most educational institutions manually grade coding assignments completed by students \cite{}. Manual evaluaton of code takes a great deal of time and is prone to bad evaluations due to the substantial amount of different ways a program can be written. Sometimes, this leads the grader to only evaluate the program's output based on a specific input.

Panda Code Reviews is a web-based automatic code grader. The main objetive of this project is to design and build a fully hosted application for eliminating the difficulties that come with grading software assignments. The application design is shown throughout this progress report. Implementation phase has already begun and is already residing on the cloud.

This report will discuss several things. First, it contains a schedule analysis that explains any changes within the proposed timeline, followed by a review of the current expenses and budget analysis. The next section contains the project technical plan, which includes the software design. An overview of the system is given, followed by a more detailed breakdown of the software components. The software progress report includes a high level software description, software architecture, communication interfaces, and the software implementation assessment. Finally, this report indicates proposal deviations and a collection of appendices in order to provide a greater level of detail for the different design specifications.