\autsection{Progress}{Nelián Colón}

%analyzes current status with regard to proposed timeline

%lists and describes what has been completed or achieved

%lists and describes what has not been completed or has not started with regard
%to the proposed timeline

%links or refers to up-to-date Gantt char (MS project file)

%when delayed, presents corrective measures taken or a realistic contingency
%plan to complete the project on time.

In compliance with the proposed timeline, the design phase was completed in time
and Panda Code Reviews is currently in the software implementation phase of its
individual components. Instead of creating user interface mockups as planned,
the team decided to build static pages with HTML and CSS. This allowed the team
to start the implementation of the front end earlier than projected.
Additionally, a prototype for compiling and running Java code has been
developed. The code is uploaded to the server via the web application at its
front end interface. The front end passes the uploaded code to the back end with
the compilation and execution query, and the back end executes the instruction,
runs the code and outputs the result back to the front end, which then displays
the results to the user. The progress of the current implementation of the front
end can be seen in the screen shots provided in the Appendix.

Please refer to the Gantt chart, which is included in a separate file, to see
changes in schedule and tasks distribution. The Gantt chart file also contains
the tasks that have been completed and the percentage of completion of the tasks
that have been started. The most important change to the schedule is that the
implementation of the revenue system with Google Adsense cannot be started until
there is enough content in the website and the team has acquired a domain name.
These are requirements of Google Adsense that have not yet been met. The plan of
the team is to continue the timeline established in the revised Gantt Chart.
